---
title: "Dissertation"
author: "Daniela Escudero Ambrosi"
date: "`r Sys.Date()`"
output: html_document
---

```{r, eval=TRUE}

```

## Libraries
```{r, eval=TRUE}

# Install packages
#install.packages("f1dataR") #Formula 1

# Libraries
library(reticulate)
library(f1dataR)
library(dplyr)
library(flexmix)

```

## F1PI
```{r, eval=TRUE}

########################
### F1 Power Index
########################

y = 2023 #year
n = nrow(load_schedule(y)) #session number

driv_const <- as.data.frame(load_standings(y, n))[, -c(2,3,4)] #DF of drivers and constructors
finished <- c("Finished", "+1 Lap", "+2 Laps") #Finished status
last_results <- load_standings(y-1) #Last year results
last_results[,2:4] <- lapply(last_results[, 2:4], as.numeric) #Turning values to numeric
points <- sort(dgamma(seq(0.5,3, length.out = 20), shape = 1, rate = 1), decreasing = T) * 40 #PI points

# Points plot
plot(seq(1, 20, by = 1), points, type = "b", xlab = "Driver position", ylab = "Points", col = "orangered3", lwd = 3, ylim = c(-1, 26), xaxt = "n")
points(seq(1, 20, by = 2), c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1), type = "b", lwd = 3, col = "springgreen3")
legend("topright", legend = c("FIA points", "Computed points"), lwd = 3, col = c("springgreen3", "orangered3"), bty="n",cex = 0.8)
axis(3, seq(1, 20, by = 2), lwd = 3, col = "springgreen3", labels = 1:10)
axis(1, 1:20, lwd = 3, col = "orangered3")
mtext(c("Comparison between FIA awarded points and new computed Points"), side = 3, line = -1, outer = TRUE, font = 2, cex = 1.3)

# Results
assign(paste("Results_DF", y, sep = "_"), data.frame())
Results_DF <- get(paste("Results_DF", y, sep = "_"))
for(k in 1:n){ #Sessions
  Results <- as.data.frame(load_results(y, k))[,-c(3,6,8:12)]
  Results$points <- points
  Results$round <- rep(k,20)
  Results_DF <- bind_rows(Results_DF, Results)
}
assign(paste("Results_DF", y, sep = "_"), Results_DF)

# New points
drivers_const_DF <- data.frame()
for (i in 1:n){
  round <- i
  for (j in 1:20){
    driver <- Results_DF[j+(20*(round-1)), 1]
    constructor <- driv_const[driv_const$driver_id == driver, 2] #corresponding constructor
    round_points <- Results_DF[Results_DF$round == round & Results_DF$driver_id == driver,]$points
    accumulated_points <- sum(Results_DF[Results_DF$round %in% 1:round & 
                      Results_DF$driver_id == driver,]$points)
    x <- data.frame(driver, constructor, round_points, accumulated_points, round)
    drivers_const_DF <- bind_rows(drivers_const_DF, x)
  }
}

# Results from the parameter tuning
a = 1 #gamma
b = 0.02 #zeta
c = 0.58 #eta
d = 0.98 #theta
e = 0.9 #nu

# F1 Power Index for the race
F1PI_DF <- data.frame()
for (i in 1:n){
  round <- i
  for (j in 1:20){
    driver <- Results_DF[j+(20*(round-1)), 1]
    constructor <- driv_const[driv_const$driver_id == driver, 2] #corresponding constructor
    status <- Results_DF[j+(20*(round-1)), 5]
    driv_accum <- drivers_const_DF[drivers_const_DF$round == round & 
                                     drivers_const_DF$driver == driver,]$accumulated_points
    const_accum <- sum(drivers_const_DF[drivers_const_DF$round == round & 
                                     drivers_const_DF$constructor == constructor,]$accumulated_points)
    avail_accum <- sum(drivers_const_DF[drivers_const_DF$round == round,]$accumulated_points)
    
    # Power Index
    PI <- ((driv_accum * a + const_accum * (1-a)) / (avail_accum * a + avail_accum * (1-a) * 2)) * 100
    
    # Adjusting for round 1
    if(round == 1){
      if(status %in% finished){
        PI_adj <- PI * b + 
          (sum(last_results[last_results$constructor_id == constructor,]$points)/sum(last_results$points)) * 100 * (1-b)
      } else{
        PI_adj <- PI * c + 
          (sum(last_results[last_results$constructor_id == constructor,]$points)/sum(last_results$points)) * 100 * (1-c)
      }
    } else if(status %in% finished){ # Averaging for last race
         PI_adj <- PI * d + tail(F1PI_DF[F1PI_DF$driver == driver,]$PI_adj, n = 1) * (1-d)
       } else{ # Adjusting for incidents
      PI_adj <-  PI * e + tail(F1PI_DF[F1PI_DF$driver == driver,]$PI_adj, n = 1) * (1-e)
    }
    
    PI_x <- data.frame(driver, constructor, status, PI, PI_adj, round)
    F1PI_DF <- bind_rows(F1PI_DF, PI_x)
  }
}

# Master DATASET

assign(paste("masterDataSet", y, sep = ""), cbind.data.frame(Results_DF[,c(1,2,7,4,3,5)], as.numeric(Results_DF[,4]) - as.numeric(Results_DF[,3]), drivers_const_DF[,c(3,4)], F1PI_DF[,c(4,5)]))

write.csv(paste("masterDataSet", y, sep = ""), paste("DataSet", y, ".csv", sep = ""), row.names = FALSE)

```

## Method -- FUNCTION
```{r, eval=TRUE}

places_difference <- function(driver, round){ ### Round MUST be >= 2
  grid <- as.integer(Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$grid) #In the future, to make predictions, this argument MUST be given in the function
  constructor <- driv_const[driv_const$driver_id == driver, 2] #corresponding constructor
  team_mate <- driv_const[driv_const$constructor_id == constructor & 
                            !(driv_const$driver_id %in% c(driver, "de_vries", "hulkenberg")), 1]
  last_PI <- ifelse(is.nan(tail(F1PI_DF[F1PI_DF$driver == driver &
                                            F1PI_DF$round %in% 1:(round-1),]$PI_adj, n = 1)), 0, 
                      tail(F1PI_DF[F1PI_DF$driver == driver & F1PI_DF$round %in% 1:(round-1),]$PI_adj, n = 1))
  accumulated_points_d <- sum(drivers_const_DF[drivers_const_DF$driver == driver &
                                             drivers_const_DF$round %in% 1:(round-1),]$round_points)
  accumulated_points_c <- sum(drivers_const_DF[drivers_const_DF$constructor == constructor 
                                             & drivers_const_DF$round %in% 1:(round-1),]$round_points)
  status <- Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$status
  actual_place <- ifelse(Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$status %in% finished,
                         Results_DF[Results_DF$driver_id == driver & Results_DF$round == round, 3], "DNF")
  avg_tm_points <- ifelse(is.nan(mean(drivers_const_DF[drivers_const_DF$driver == team_mate & drivers_const_DF$round %in% 1:(round-1),]$round_points)), mean(drivers_const_DF[drivers_const_DF$constructor == constructor & drivers_const_DF$round %in% 1:(round-1),]$round_points) , mean(drivers_const_DF[drivers_const_DF$driver == team_mate & drivers_const_DF$round %in% 1:(round-1),]$round_points))
  #average teammate's points, CETERIS PARIBUS we're assuming they will score the same in average. If there's a NaN, we'll consider the team avg points
  
  # Minimizing the change in PI
  x <- c()
  for(i in 1:20){
    projected_points <- points[i]
    projected_PI_single <- (((accumulated_points_d + projected_points) * a +
      (accumulated_points_c + projected_points + avg_tm_points) * (1-a)) /
        ((sum(points) * round * a) + (sum(points)* 2 * round * (1-a)))) * 100
    projected_PI <- projected_PI_single * d + last_PI * (1-d)
    diference <- abs(last_PI - projected_PI)
    x <- rbind(x, diference)
  }
  
  mean_grid <- ifelse(driver == "vettel" & round == 3, 0,
                      median(as.integer(Results_DF[Results_DF$driver_id == driver &
                                                   Results_DF$round %in% 1:(round-1),]$grid)))
  sd_grid <- ifelse(round == 2 | is.na(sd((as.integer(Results_DF[Results_DF$driver_id == driver &
                                                               Results_DF$round %in% 1:(round-1),]$grid)))), 0,
                    sd((as.integer(Results_DF[Results_DF$driver_id == driver &
                                                               Results_DF$round %in% 1:(round-1),]$grid))))
  if(abs(grid - mean_grid) <= sd_grid){
    places <- as.numeric(Results_DF[Results_DF$driver_id == driver & Results_DF$round %in% 1:(round-1), 4]) -
      as.numeric(Results_DF[Results_DF$driver_id == driver & Results_DF$round %in% 1:(round-1), 3])
    lambda_p <- ifelse(length(places[places >= 0]) == 0, 100, sum(places[places >= 0]) / length(places[places >= 0]))
    lambda_n <- ifelse(length(places[places < 0]) == 0, -100, sum(places[places < 0]) / length(places[places < 0]))
    
    z <- c()
    if (lambda_p != 100){
      z[1:grid] <- 1-dpois(c((grid - 1):0), lambda_p)
    } else {
      z[1:grid] <- 1
    }
    
    if (lambda_n != -100 & grid < 20){
      z[(grid+1):20] <- 1-dpois(c(1:(20-grid)), abs(lambda_n))
    } else if (grid < 20){
      z[(grid+1):20] <- 1
    }
    
    predicted <- which.min(x*z)
    } else{
      predicted <- which.min(x)}
  
  prediction <- paste("Starting place: ", grid, ", Projected final place: ", predicted,
                       ", Actual place: ", actual_place, sep = "")

  #return(prediction)
  return(predicted)
}


# Test
driver = "hamilton"
round = 10

places_difference(driver, round)

```

## Predict for the whole grid
```{r, eval=TRUE}

predictions_grid <- data.frame()

round = 10
for(i in 1:20){
    predictions_grid[i,1] <- driv_const[i,1]
    predictions_grid[i,2] <- as.numeric(Results_DF[Results_DF$driver_id == driv_const[i,1] & Results_DF$round == round, ]$position)
    predictions_grid[i,3] <- places_difference(driv_const[i,1], round)
}

colnames(predictions_grid) <- c("Driver", "Actual Result", "Predicted")

predictions_grid

```

## Predict 1-1
```{r, eval=TRUE}

predict_grid <- function(round){
  stand <- load_standings(y, round-1) ###YEAR SOULD BE A PARAMETER IN THE FUTURE
  drivers <- Results_DF[Results_DF$round == round,]$driver_id
  
  predictions_1 <- data.frame(drivers)
  for(i in 1:20){
    predictions_1[i,2] <- places_difference(drivers[i], round)
  }
  
  predictions <- data.frame(1:20)
  for (i in 1:20) {
    #Function 1
    if (table(predictions_1[predictions_1$V2 == min(predictions_1[,2]),2]) > 1){
      predictions[i,2] <- stand[stand$driver_id %in% predictions_1[predictions_1$V2 == min(predictions_1[,2]), 1],][1]
      predictions_1[predictions_1$drivers == predictions[i,2], 2] <- 30
    }
    
    else{
      predictions[i,2] <- predictions_1[predictions_1$V2 == min(predictions_1[,2]), 1]
      predictions_1[predictions_1$drivers == predictions[i,2], 2] <- 30
    }
    
  }
    colnames(predictions) <- c("predicted_position", "function_1")
  
  
  #Error
  xx <- data.frame()
  for (i in 1:20){
    driver_x <- Results_DF[Results_DF$round == round,]$driver_id[i]
    status <- Results_DF[Results_DF$round == round,]$status[i]
    diference_1 <- abs(predictions[predictions$function_1 == driver_x, 1] - i)
    diference_2 <- abs(predictions[predictions$function_2 == driver_x, 1] - i)
    if(!(status %in% finished) || driver_x == "de_vries"){
      xx[i,1] <- 0
    }
    else if (diference_1 == 1){
      xx[i,1] <- 0.5
    }
    else if (diference_1 >= 1){
      xx[i,1] <- 1
    }
    else{
      xx[i,1] <- 0
    }
  }
  
  error_f1 <- sum(xx[,1])
  
  predictions <- cbind(predictions, Results_DF[Results_DF$round == round,]$driver_id)
  colnames(predictions) <- c("predicted_position", "function_1", "real_position")
  predictions[21,] <- c(0, error_f1,0)
  
  return(predictions)
}


predict_grid(10)


```



## MSE (without accidents)
```{r, eval=TRUE}

# MSE
xx <- c() #new vector
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id #driver
  round_x <- Results_DF[i,]$round #round
  position <- as.integer(Results_DF[i,]$position) #real position
  status <- Results_DF[i, 5] #status
  
  if(driver_x == "de_vries" | !(status %in% finished)){ #if not in status
    xx[i-20] <- 0
  } else{
    xx[i-20] <- (places_difference(driver_x, round_x) - position)^2 #squarred difference
    }
  }
mse <- sum(xx)/length(xx) #MSE

cat("The MSE is", mse)  #Printing the result

# 7.75

```

## MSE per race (without accidents)
```{r, eval=TRUE}

# MSE per race

mse_race <- c()
for (i in 1:21){
  xx <- c() #new vector
  for (j in ((i*20)+1):((i*20)+20)){
    driver_x <- Results_DF[j,]$driver_id #driver
    round_x <- Results_DF[j,]$round #round
    position <- as.integer(Results_DF[j,]$position) #real position
    status <- Results_DF[j, 5] #status
    
    if(driver_x == "de_vries" | !(status %in% finished)){ #if not in status
      xx[j-(i*20)] <- -100
    } else{
      xx[j-(i*20)] <- (places_difference(driver_x, round_x) - position)^2 #squared difference
      }
    }
  mse_race <- cbind(mse_race, sum(xx[xx != -100])/length(xx[xx != -100])) #MSE
}


## Plot

# Add the regression line
sqrt_mse_race <- as.numeric(sqrt(mse_race))
race_numbers <- as.numeric(c(1:21))
regression <- lm(sqrt_mse_race ~ race_numbers)

plot(race_numbers, sqrt_mse_race, type ="o", lwd = 3, xaxt = "n", xlab = "Race number", ylab = "RMSE", main = c("RMSE per race: average difference between ", " the prediction and result per driver"), col = "springgreen3")
axis(1, at = 1:21, labels = c(2:22))
abline(regression, col = "orangered3", lwd = 3)
legend("topright", legend = c("RMSE","Trend"), lwd = 3, col = c("springgreen3","orangered3"),bty="n",cex=0.8)

```


## Minimizing MSE
```{r, eval=TRUE}

# This function minimizes the squared sum of errors.

dif <- function(a = 1, b = 0, c = 0.6, d = 1, e = 1){
  
  ### 1. F1 POWER INDEX CALCULATION
  F1PI_DF <- data.frame()
  for (i in 1:n){
    round <- i
    for (j in 1:20){
      driver <- Results_DF[j+(20*(round-1)), 1]
      constructor <- driv_const[driv_const$driver_id == driver, 2] #corresponding constructor
      status <- Results_DF[j+(20*(round-1)), 5]
      driv_accum <- drivers_const_DF[drivers_const_DF$round == round & 
                                       drivers_const_DF$driver == driver,]$accumulated_points
      const_accum <- sum(drivers_const_DF[drivers_const_DF$round == round & 
                                       drivers_const_DF$constructor == constructor,]$accumulated_points)
      avail_accum <- sum(drivers_const_DF[drivers_const_DF$round == round,]$accumulated_points)
      
      # Power Index
      PI <- ((driv_accum * a + const_accum * (1-a)) / (avail_accum * a + avail_accum * (1-a) * 2)) * 100
      
      # Adjusting for round 1, and vettel and de vries debut
      if(round == 1 | driver == "vettel" & round == 3 | driver == "de_vries"){
        if(status %in% finished){
          PI_adj <- PI * b + 
            (sum(last_results[last_results$constructor_id == constructor,]$points)/sum(last_results$points)) * 100 * (1-b)
        } else{
          PI_adj <- PI * c + 
            (sum(last_results[last_results$constructor_id == constructor,]$points)/sum(last_results$points)) * 100 * (1-c)
        }
      } else if(status %in% finished){ # Averaging for last race
           PI_adj <- PI * d + tail(F1PI_DF[F1PI_DF$driver == driver,]$PI_adj, n = 1) * (1-d)
         } else{ # Adjusting for incidents
        PI_adj <-  PI * e + tail(F1PI_DF[F1PI_DF$driver == driver,]$PI_adj, n = 1) * (1-e)
      }
      
      PI_x <- data.frame(driver, constructor, status, PI, PI_adj, round)
      F1PI_DF <- bind_rows(F1PI_DF, PI_x)
    }
  }

  
  # 2. PREDICTIVE FUNCTION
  places_difference <- function(driver, round){ ### Round MUST be >= 2
    grid <- as.integer(Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$grid) #In the future, to make predictions, this argument MUST be given in the function
    constructor <- driv_const[driv_const$driver_id == driver, 2] #corresponding constructor
    team_mate <- driv_const[driv_const$constructor_id == constructor & 
                              !(driv_const$driver_id %in% c(driver, "de_vries", "hulkenberg")), 1]
    last_PI <- ifelse(is.nan(tail(F1PI_DF[F1PI_DF$driver == driver &
                                              F1PI_DF$round %in% 1:(round-1),]$PI_adj, n = 1)), 0, 
                        tail(F1PI_DF[F1PI_DF$driver == driver & F1PI_DF$round %in% 1:(round-1),]$PI_adj, n = 1))
    accumulated_points_d <- sum(drivers_const_DF[drivers_const_DF$driver == driver &
                                               drivers_const_DF$round %in% 1:(round-1),]$round_points)
    accumulated_points_c <- sum(drivers_const_DF[drivers_const_DF$constructor == constructor 
                                               & drivers_const_DF$round %in% 1:(round-1),]$round_points)
    status <- Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$status
    actual_place <- ifelse(Results_DF[Results_DF$driver_id == driver & Results_DF$round == round,]$status %in% finished,
                           Results_DF[Results_DF$driver_id == driver & Results_DF$round == round, 3], "DNF")
    avg_tm_points <- ifelse(is.nan(mean(drivers_const_DF[drivers_const_DF$driver == team_mate & drivers_const_DF$round %in% 1:(round-1),]$round_points)), mean(drivers_const_DF[drivers_const_DF$constructor == constructor & drivers_const_DF$round %in% 1:(round-1),]$round_points) , mean(drivers_const_DF[drivers_const_DF$driver == team_mate & drivers_const_DF$round %in% 1:(round-1),]$round_points))
    #average teammate's points, CETERIS PARIBUS we're assuming they will score the same in average. If there's a NaN, we'll consider the team avg points
    
    # Minimizing the change in PI
    x <- c()
    for(i in 1:20){
      projected_points <- points[i]
      projected_PI_single <- (((accumulated_points_d + projected_points) * a +
        (accumulated_points_c + projected_points + avg_tm_points) * (1-a)) /
          ((sum(points) * round * a) + (sum(points)* 2 * round * (1-a)))) * 100
      projected_PI <- projected_PI_single * d + last_PI * (1-d)
      diference <- abs(last_PI - projected_PI)
      x <- rbind(x, diference)
    }
    
    mean_grid <- ifelse(driver == "de_vries" | driver == "vettel" & round == 3, 0,
                        median(as.integer(Results_DF[Results_DF$driver_id == driver &
                                                     Results_DF$round %in% 1:(round-1),]$grid)))
    sd_grid <- ifelse(round == 2 | is.na(sd((as.integer(Results_DF[Results_DF$driver_id == driver &
                                                                 Results_DF$round %in% 1:(round-1),]$grid)))), 0,
                      sd((as.integer(Results_DF[Results_DF$driver_id == driver &
                                                                 Results_DF$round %in% 1:(round-1),]$grid))))
    if(abs(grid - mean_grid) <= sd_grid){
      places <- as.numeric(Results_DF[Results_DF$driver_id == driver & Results_DF$round %in% 1:(round-1), 4]) -
        as.numeric(Results_DF[Results_DF$driver_id == driver & Results_DF$round %in% 1:(round-1), 3])
      lambda_p <- ifelse(length(places[places >= 0]) == 0, 100, sum(places[places >= 0]) / length(places[places >= 0]))
      lambda_n <- ifelse(length(places[places < 0]) == 0, -100, sum(places[places < 0]) / length(places[places < 0]))
      
      z <- c()
      if (lambda_p != 100){
        z[1:grid] <- 1-dpois(c((grid - 1):0), lambda_p)
      } else {
        z[1:grid] <- 1
      }
      
      if (lambda_n != -100 & grid < 20){
        z[(grid+1):20] <- 1-dpois(c(1:(20-grid)), abs(lambda_n))
      } else if (grid < 20){
        z[(grid+1):20] <- 1
      }
      
      predicted <- which.min(x * (z^2))
      } else{
        predicted <- which.min(x)}
    
    return(predicted)
  }
  
  
  #MSE
  xx <- c() #new vector
  for (i in 61:nrow(Results_DF)){
    driver_x <- Results_DF[i,]$driver_id #driver
    round_x <- Results_DF[i,]$round #round
    position <- as.integer(Results_DF[i,]$position) #real position
    status <- Results_DF[i, 5] #status
    
    if(driver_x == "de_vries" | !(status %in% finished)){ #if not in status
      xx[i-60] <- 0
    } else{
      xx[i-60] <- (places_difference(driver_x, round_x) - position)^2 #squarred difference
      }
    }
  mse <- sum(xx)/length(xx) #MSE

  return(mse)
}

##### 1- First grid
min_parameters <- expand.grid("a" = seq(0, 1, by = 0.2), "b" = seq(0, 1, by = 0.2),
                              "c" = seq(0, 1, by = 0.2), "d" = seq(0, 1, by = 0.2),
                              "e" = seq(0, 1, by = 0.2))
Error <- apply(min_parameters, 1, function(x) dif(a = x[1], b = x[2], c = x[3], d = x[4], e = x[5])) #Applying the function
min_parameters[which.min(Error),] # Minimum parameters: (1, 0, 0.6, 1, 1), error = 7.8


##### 2- Second grid
min_parameters_2 <- expand.grid("a" = seq(0.8, 1, by = 0.05), "b" = seq(0, 0.7, by = 0.05),
                              "c" = seq(0.5, 0.7, by = 0.05), "d" = seq(0.8, 1, by = 0.05),
                              "e" = seq(0.8, 1, by = 0.05))
Error_2 <- apply(min_parameters_2, 1, function(x) dif(a = x[1], b = x[2], c = x[3], d = x[4], e = x[5])) #Applying the function
min_parameters_2[which.min(Error_2),] # Minimum parameters: (1, 0, 0.6, 1, 0.9), error = 7.757895



##### 2- Third grid
min_parameters_3 <- expand.grid("a" = seq(0.98, 1, by = 0.005), "b" = c(seq(0, 0.07, by = 0.01), seq(0.49, 0.61, by = 0.02)),
                              "c" = seq(0.57, 0.62, by = 0.01), "d" = c(seq(0.78, 0.82, by = 0.01), seq(0.95, 1, by = 0.01)),
                              "e" = seq(0.88, 0.92, by = 0.01))
Error_3 <- apply(min_parameters_3, 1, function(x) dif(a = x[1], b = x[2], c = x[3], d = x[4], e = x[5])) #Applying the function
min_parameters_3[which.min(Error_3),] # Minimum parameters: (0.99, 0.02, 0.58, 0.98, 0.9), error = 7.705263


# Renaming parameters
a = min_parameters_3[which.min(Error_3), 1]
b = min_parameters_3[which.min(Error_3), 2]
c = min_parameters_3[which.min(Error_3), 3]
d = min_parameters_3[which.min(Error_3), 4]
e = min_parameters_3[which.min(Error_3), 5]


# Plot
plot(Error, type ="l", lwd = 0.2, xaxt = "n", xlab = "Parameters combination", ylab = "MSE", main = "Combination of parameters that optimize the MSE", col= "springgreen3",xlim=c(0,7800))
lines(1:length(Error), rep(7.705263, length(Error)), type = "l", lwd = 4, col = "orangered3", lty = 3)
points(which.min(Error), min(Error_3), col = "dodgerblue4", pch = 4, lwd = 4, cex = 1.7)
legend("topright", legend = c("Combinations","Minimum MSE","Optimum"), col = c("springgreen3","orangered3","dodgerblue4"),bty="n",cex=0.7,lwd = 2)

```

## Error rate (without accidents) - Exact values
```{r, eval=TRUE}

# Accuracy for exact places
xx <- c()
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id
  round_x <- Results_DF[i,]$round
  position <- as.integer(Results_DF[i,]$position)
  status <- Results_DF[i, 5]
  diference <- abs(places_difference(driver_x, round_x) - position)
  if(!(status %in% finished)){
    xx[i-20] <- 10
  } else if (diference != 0){
    xx[i-20] <- 1
  } else{
    xx[i-20] <- 0
  }
}

# Accuracy
acc <- (length(xx[xx != 10]) - sum(xx[xx != 10])) / length(xx[xx != 10]) * 100

cat("The accuracy for exact places is ", acc)  #Printing the result

#14.70

```

## Error rate (without accidents) - +- 1 place
```{r, eval=TRUE}

# Accuracy for +- 1 place
xx <- c()
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id
  round_x <- Results_DF[i,]$round
  position <- as.integer(Results_DF[i,]$position)
  status <- Results_DF[i, 5]
  diference <- abs(places_difference(driver_x, round_x) - position)
  if(!(status %in% finished)){
    xx[i-20] <- 10
  } else if (diference > 1){
    xx[i-20] <- 1
  } else{
    xx[i-20] <- 0
  }
}

# Accuracy
acc <- (length(xx[xx != 10]) - sum(xx[xx != 10])) / length(xx[xx != 10]) * 100

cat("The accuracy for +- 1 place is ", acc)  #Printing the result

# 43.80403

```

## Error rate (without accidents) - +- 2 places
```{r, eval=TRUE}

# Accuracy for +- 2 places
xx <- c()
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id
  round_x <- Results_DF[i,]$round
  position <- as.integer(Results_DF[i,]$position)
  status <- Results_DF[i, 5]
  diference <- abs(places_difference(driver_x, round_x) - position)
  if(!(status %in% finished)){
    xx[i-20] <- 10
  } else if (diference > 2){
    xx[i-20] <- 1
  } else{
    xx[i-20] <- 0
  }
}

# Accuracy
acc <- (length(xx[xx != 10]) - sum(xx[xx != 10])) / length(xx[xx != 10]) * 100

cat("The accuracy for +- 2 places is ", acc)  #Printing the result

# 60.51873

```

## Error rate (without accidents) - +- 3 places
```{r, eval=TRUE}

# Accuracy for +- 3 places
xx <- c()
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id
  round_x <- Results_DF[i,]$round
  position <- as.integer(Results_DF[i,]$position)
  status <- Results_DF[i, 5]
  diference <- abs(places_difference(driver_x, round_x) - position)
  if(!(status %in% finished)){
    xx[i-20] <- 10
  } else if (diference > 3){
    xx[i-20] <- 1
  } else{
    xx[i-20] <- 0
  }
}

# Accuracy
acc <- (length(xx[xx != 10]) - sum(xx[xx != 10])) / length(xx[xx != 10]) * 100

cat("The accuracy for +- 3 places is", acc)  #Printing the result

# 75.21614

```
## Error rate (without accidents) - 10 +- 3 places
```{r, eval=TRUE}

# Accuracy for +- 3 places
xx <- c()
for (i in 21:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id
  round_x <- Results_DF[i,]$round
  position <- as.integer(Results_DF[i,]$position)
  status <- Results_DF[i, 5]
  diference <- abs(places_difference(driver_x, round_x) - position)
  if(!(status %in% finished)){
    xx[i-20] <- 10
  } else if (diference > 3  & position < 11){
    xx[i-20] <- 1
  } else{
    xx[i-20] <- 0
  }
}

# Accuracy
acc <- (100 - sum(xx[xx != 10]))

cat("The accuracy for the 10 first places +- 3 places is ", acc)  #Printing the result

# 75.50432

```



## Proposed evaluation - NOT INCLUDED
```{r, eval=TRUE}

# Evaluation error
xx <- c() #new vector
for (i in 61:nrow(Results_DF)){
  driver_x <- Results_DF[i,]$driver_id #driver
  round_x <- Results_DF[i,]$round #round
  position <- as.integer(Results_DF[i,]$position) #real position
  status <- Results_DF[i, 5] #status
  
  if(driver_x == "de_vries" | !(status %in% finished)){ #if not in status
    xx[i-60] <- 0
  } else{
    xx[i-60] <- abs(places_difference(driver_x, round_x) - position)/10
    }
  }
err <- sum(xx)

cat("The error of our new evaluation method is", err)  #Printing the result

# 78.5

```
